### 2020-03-03 CalNotes.tex
CLT 2

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
		J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) &= \sqrt{T} \left( I_1^\epl(T) - \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\mathfrak p_\epl \right) \\
	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
	\end{aligned}
	\end{equation}
	In order to treat the terms $J_{1,1}^\epl(T)$ and $J_{1,2}^\epl(T)$, we will employ a technique presented in \cite[Remark 6.17]{PaS08}. Denoting by $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
	\begin{equation}
		\mathcal L^\epl = -\left(V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx},
	\end{equation}
	let $\Phi^\epl$ the solution of the Poisson equation
	\begin{equation}\label{eq:CLT_Poisson}
		\mathcal L^\epl \Phi^\epl(x, z) = \chi(x, z) - \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)].
	\end{equation}	
	where $\chi$ is a sufficiently smooth function. Then, an application of Itô formula  yields
	\begin{equation}
	\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
	\end{equation}
	where
	\begin{equation}
		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
	\end{equation}
	Let us consider $J_{1,1}^\epl(T)$ and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
	\begin{equation}
		\chi(x, z) = 
	\end{equation}

@@

	Therefore, we have
%	\begin{equation}
%	\begin{aligned}
%		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
%		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
%	\end{aligned}
%	\end{equation}
	\begin{equation}
		J_{1,1}^\epl(T)= \sqrt{T} \mathcal M_\epl^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
	\end{equation}
	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get
%	\begin{equation}
%		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
%	\end{equation}
	\begin{equation}
		\lim_{T \to \infty} \frac{\mathcal M_\epl^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q_T^\epl$, we get 
%	\begin{equation}
%		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
%	\end{equation}
	\begin{equation}
	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\mathcal M_\epl^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by
	\begin{equation}
		\Gamma_1^\epl = 2\sigma \mathcal M^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M^{-\top}.
	\end{equation}
	\corr{For the second part of \eqref{eq:decomposition_first_term} we follow a similar procedure defining a different Poisson equation. The argument has to be slightly modified because we have to work with random matrix rather than random vector, but finally we obtain a second Gaussian term $\mathcal N(0, \Gamma_2^\epl)$. Therefore, we have to study the limit as $\epl$ goes to zero of the covariance matrices $\Gamma_1^\epl$ and $\Gamma_2^\epl$, which depend on the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$ of the Poisson problems.} \\

>>>>

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
		J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) &= \sqrt{T} \left( I_1^\epl(T) - \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\mathfrak p_\epl \right) \\
	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
	\end{aligned}
	\end{equation}
	In order to treat the terms $J_{1,1}^\epl(T)$ and $J_{1,2}^\epl(T)$, we will employ a technique presented in \cite[Remark 6.17]{PaS08}. Denoting by $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
	\begin{equation}
		\mathcal L^\epl = -\left(V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx},
	\end{equation}
	let $\Phi^\epl$ the solution of the Poisson equation
	\begin{equation}\label{eq:CLT_Poisson}
		\mathcal L^\epl \Phi^\epl(x, z) = \chi(x, z) - \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)].
	\end{equation}	
	where $\chi$ is a sufficiently smooth function. Then, an application of Itô formula  yields
	\begin{equation}
	\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
	\end{equation}
	where
	\begin{equation}
		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
	\end{equation}
	Let us consider $J_{1,1}^\epl(T)$, which can be written
	\begin{equation}
	J_{1,1}^\epl(T) = \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( \frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \mathfrak p_\epl \right),
	\end{equation}
	and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
	\begin{equation}
		\chi(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z).
	\end{equation}

@@

	Therefore, we have
%	\begin{equation}
%	\begin{aligned}
%		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
%		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
%	\end{aligned}
%	\end{equation}
	\begin{equation}
		J_{1,1}^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
	\end{equation}
	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem
%	\begin{equation}
%		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
%	\end{equation}
	\begin{equation}
		\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q_T^\epl$ and employing the ergodic theorem, we get 
%	\begin{equation}
%		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
%	\end{equation}
	\begin{equation}
	\lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by
	\begin{equation}
		\Gamma_1^\epl = 2\sigma \mathcal M^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M^{-\top}.
	\end{equation}
	\corr{For the second part of \eqref{eq:decomposition_first_term} we follow a similar procedure defining a different Poisson equation. The argument has to be slightly modified because we have to work with random matrix rather than random vector, but finally we obtain a second Gaussian term $\mathcal N(0, \Gamma_2^\epl)$. Therefore, we have to study the limit as $\epl$ goes to zero of the covariance matrices $\Gamma_1^\epl$ and $\Gamma_2^\epl$, which depend on the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$ of the Poisson problems.} \\
